Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Add lines of code for applications
Add data sets

\begin{table}
\small
\centering
\begin{tabular}{ l c c c c }
App. & resizing barriers & kill & fork & transmit vars\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 & 0 & 4\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 & 0 & 0\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 & 0 & 3\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 & 0 & 0 \\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 & 0  & 4 \\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 & 0  & 4 \\
\rowcolor{Gray3}
octree & 0 / 0 & 1 & 1 & 0\\
\rowcolor{Gray3}
game & 0 / 0 & 1 & 1 & 0\\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

\ADComment{It might be good to add a LOC column to \mytab\ref{tab:applications} to indicate how large the original versions of these applicaitons were.}

@@

\ADComment{We need to say something about the number of data sets
  associated with each application, so that we know the total number
  of application/data-set pairs.}

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia~\cite{...} and Lonestar~\cite{...} GPU application suites,
using global barriers.  We indicate how many of the original number of barriers are changed to resizing barriers, and how many variables need to
be transmitted.  In all cases all barriers were converted, except for bc
which contains barriers deeper in the call stack, a case not supported
by our prototype. Still, these barriers could in principle also be
converted.  The remaining 2 algorithms are workstealing applications:
each required the addition of $\offerfork$ and $\offerkill$ at the start
of the main loop, and no variables needed to be transmitted. For all
these examples the porting to cooperative kernels was similarly straightforward to the porting illustrated in \mysec\ref{sec:programmingguidelines} for our running examples, and did not require reshaping of the original algorithm.

@@

\begin{table}
\small
\centering
\begin{tabular}{ l l l l }
Chip & HD520 & HD5500 & Iris\\
\hline
\# compute units  & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
Driver   & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
Host CPU & \ADComment{...} & \ADComment{...} & \ADComment{...} \\
\end{tabular}
\caption{The Intel GPU platforms used in our evaluation}
\label{tab:chipstested}
\end{table}

>>>>

\begin{table}
\small
\centering
\begin{tabular}{ l c c c c c c}
App. & resizing barr. & kill & fork & transmit & LoC & data sets\\
\hline
\rowcolor{Gray1}
color & 2 / 2 & 0 & 0 & 4 & 55 & 2\\
\rowcolor{Gray1}
mis & 3 / 3 & 0 & 0 & 0 & 71 & 2\\
\rowcolor{Gray1}
bc & 3 / 6 & 0 & 0 & 3 & 150 & 2\\
\rowcolor{Gray1}
p-sssp & 3 / 3 & 0 & 0 & 0  & 42 & 1\\
\rowcolor{Gray2}
bfs & 2 / 2 & 0 & 0  & 4  & 185 & 2\\
\rowcolor{Gray2}
l-sssp & 2 / 2 & 0 & 0  & 4  & 196 & 2\\
\rowcolor{Gray3}
octree & 0 / 0 & 1 & 1 & 0 & 213 & 1 \\
\rowcolor{Gray3}
game & 0 / 0 & 1 & 1 & 0 & 308 & 1 \\
\end{tabular} \\
\vspace{.2cm}
\crule[Gray1]{.2cm}{.2cm} Pannotia \hspace{.4cm} \crule[Gray2]{.2cm}{.2cm} Lonestar GPU  \hspace{.4cm}  \crule[Gray3]{.2cm}{.2cm} work stealing
\caption{Blocking GPU applications investigated}
\label{tab:applications}
\end{table}

@@

\mytablong\ref{tab:applications} gives an overview of the 8 irregular
algorithms that we ported to cooperative kernels. Among them, 6 are
graph algorithms, based on Pannotia~\cite{...} and Lonestar~\cite{...}
GPU application suites, using global barriers.  We indicate how many of
the original number of barriers are changed to resizing barriers, and
how many variables need to be transmitted.  In all cases all barriers
were converted, except for bc which contains barriers deeper in the call
stack, a case not supported by our prototype. Still, these barriers
could in principle also be converted. The remaining 2 algorithms are
workstealing applications: each required the addition of $\offerfork$
and $\offerkill$ at the start of the main loop, and no variables needed
to be transmitted.  For all these examples the porting to cooperative
kernels was similarly straightforward to the porting illustrated in
\mysec\ref{sec:programmingguidelines} for our running examples, and did
not require reshaping of the original algorithm. Most graph applications
are executed on 2 different data sets, such that in total we have 13
application/data set pairs.

@@

\begin{table}
\small
\centering
\begin{tabular}{ l l l l }
Chip & HD520 & HD5500 & Iris\\
\hline
\# comp. units  & 24 & \ADComment{...} & \ADComment{...} \\
Driver   & 20.19.15.4501 & \ADComment{...} & \ADComment{...} \\
Host CPU & i3-6100U & \ADComment{...} & \ADComment{...} \\
\end{tabular}
\caption{The Intel GPU platforms used in our evaluation}
\label{tab:chipstested}
\end{table}
